\section{Data selection and binarization}

As my big home work assignment, I choose Neural FCA.
I have found 3 datasets with mostly categorical data, appropriate for FCA methods.

\begin{enumerate}
\item The \href{https://www.kaggle.com/datasets/rashmiranu/banking-dataset-classification}{Banking Dataset Classification} of 33000 rows.
\item A dataset of \href{https://www.kaggle.com/datasets/heeraldedhia/bike-buyers}{Bike Buyers} of 1000 rows.
\item A dataset of the \href{https://www.kaggle.com/datasets/subhajeetdas/car-acceptability-classification-dataset}{car acceptibility} (1700 rows).
\end{enumerate}

\subsubsection{Banking Dataset Classification}

The first dataset contains the economical and commercial information about the bank clients and their acceptability during current marketing campaign:

\begin{enumerate}
\item \textbf{age} - age of a person
\item \textbf{job} - type of job
\item \textbf{marital} - marital status
\item \textbf{education} - type of graduation
\item \textbf{default} - has credit in default?
\item \textbf{housing} - has housing loan?
\item \textbf{loan} - has personal loan?
\item \textbf{contact} - contact communication type ('cellular','telephone')
\item \textbf{month} - last contact month of year 
\item \textbf{day\_of\_week} - last contact day of the week
\item \textbf{duration} - last contact duration, in seconds
\item \textbf{campaign} - number of contacts performed during this campaign and for this client (includes last contact)
\item \textbf{pdays} - number of days that passed by after last contact from a previous campaign (999 if was not previously contacted)
\item \textbf{previous} -  number of contacts performed before this campaign and for this client
\item \textbf{poutcome} - outcome of the previous marketing campaign ('failure','nonexistent','success')
\item \textbf{y} - TARGET outcome of the current marketing campaign
\end{enumerate}

Features 'job', 'marital' ,'education' ,'default', 'housing' and 'loan' can have values of uncertainity. 
I decided to clear the dataset from any uncertain values and got 24305 rows of 33000
The chosen binarized features are the following:

\begin{enumerate}
\item \textbf{high\_educ} - professional skills (job = university/professional\_course)
\item \textbf{has\_job} - has a job (not a student/unemployed/retired
\item \textbf{married} - not single of divorced/widowed
\item \textbf{default}
\item \textbf{housing}
\item \textbf{loan}
\item \textbf{cell\_cont} - contacts by cellular phone 
\item \textbf{before\_con} - there were contacts performed before this campaign
\item \textbf{current\_con} - there were contacts performed during this campaign
\item \textbf{long\_dur} - the last contact was longer than the mean contact with negative result
\item \textbf{poutcome} - success of the previous campaign
\item \textbf{y} - TARGET
\end{enumerate}

Features 'default', 'housing', 'loan', and 'y' remained the same as in the dataset. 


\subsubsection{Bike Buyers}

The dataset describes potential buyers of a bike with their economic status and commuting information.

\begin{enumerate}
\item  \textbf{ID}
\item  \textbf{Marital Status}
\item  \textbf{Gender}
\item  \textbf{Income}
\item  \textbf{Children} - number of children the customer has
\item  \textbf{Education} - type of the customer graduation
\item  \textbf{Occupation} - professional level of the customer's job
\item  \textbf{Home Owner} does the customer have a real estate?
\item  \textbf{Cars} - number of cars the customer has
\item  \textbf{Commute Distance} - distance to work (several interval of miles) 
\item  \textbf{Region} - Europe/North America/ etc.
\item  \textbf{Age}
\item  \textbf{Purchased Bike} - target value of buying a bike
\end{enumerate}

According to the task priorites, the chosen features for binarization and the further FCA are: 'Income', 'Cars', 'Commute Distance', 'Gender'.
The binarized features are:

\begin{enumerate}
\item {Income 10000-60000, Income 60000-170000} - binary distribution of the income
\item {Cars 0, Cars 1-4} - binary distribution of the number of cars
\item {Commute Distance 0-1/1-2/2-5/5-10/10+ Miles} - bined distribution of the commute distance
\item {Gender Male}
\item {Purchased} = \textbf{Purchased Bike}
\end{enumerate}


\subsubsection{Car Acceptability}

The last dataset contains information of car parameters and its overall market acceptability.
Most of features are measures of car main qualities, but designed as categorical and has values 'low', 'medium', 'high and 'very high' (called 'vhigh'). 

\begin{enumerate}
\item \textbf{Buying price} - from low to very high
\item \textbf{Maintenance price} - from low to very high
\item \textbf{No\_of\_Doors} - 2,3, 4 OR 5+
\item \textbf{Person\_Capacity} - 2, 4 or more
\item \textbf{Size\_of\_Luggage} - small, medium or big
\item \textbf{Safety} - low, mdium or high
\item \textbf{Car\_Acceptability} - target value - 'unacc', 'acc', 'good', 'very good'.
\end{enumerate}

To minimize amount of unique values in columns the dataset was reduced to rows without 'vhigh' values, while acceptablity was divided into two values: $0 = unacc$ and $1 = acc-vgood$.
The datset was also stripped from features 'No\_of'\_Doors', 'Person Capacity' and 'Size of Luggage'. The remained features were binarized for each unique value.

Final set of features is the following:

\begin{enumerate}
\item \textbf{Buying Price high/low/med }
\item \textbf{Maintenance Price high/low/med}
\item \textbf{Person Capacity 2/4/more}
\item \textbf{Safety high/low/med}
\item \textbf{Car Acceptability}
\end{enumerate}


